The Unified Nature of the Dielectric Properties of Two-Dimensional Materials

### 2018-11-12 paper.tex
Change up to page 7

Eqs. \ref{eq:def-eps-1} and \ref{eq:def-eps-2}, we derive the
expressions for the in-plane and out-of-plane 2D polarizabilities,
$\alpha_{\mathrm{2D}}^{\parallel}$ and $\alpha_{\mathrm{2D}}^{\perp}$, respectively:

@@

@@

\subsection{2D Moss Relations Based on 2D Polarizabilities}
\label{sec:first-principles}
We study several types of 2D materials of different electronic and
optical properties as show in Figure \ref{fig-2}, including transition
metal dichalcogenides (TMDCs, with the formula MX\(_{\text{2}}\),
where M is a metal in group 4, 6, 10 and X=O, S, Se, Te), metal
monochalcogenides (Ga$_{2}$S$_{2}$, Ga$_{2}$Se$_{2}$), cadmium halides
(CdX$_2$, X=Cl, I), hexagonal boron nitride (BN), graphene derivatives
(fluorographene (C$_{2}$F$_{2}$), graphane (C$_{2}$H$_{2}$)),
phosphorene (P$_{4}$) and thin layer organic-inorganic perovskites
(ABX$_{3}$).  For the TMDCs, we consider 2 lattice phases, namely the
2H (P\(\bar{6}\)m2 space group) and 1T (P3m1 space group).  The static
2D polarizabilities are calculated from the static dielectric response
of the selected 2D materials using density functional theory (DFT)
with the Heyd-Scuseria-Ernzerhof hybrid functionals (HSE06) using the
Vienna Ab Initio Simulation Package (VASP) including spin-orbit
coupling to avoid limitations on the description of band gaps and
dielectric functions (see Methods for details).

Figure \ref{fig-3}a shows the calculated bandgap $E_{\mathrm{g}}$
(blue dots) and polarizabilities (bar plots) of all the 2D materials
investigated, covering a wide spectrum range from far infrared to
ultraviolet. Note from dimension analysis, it is more intuitive to
express the polarizability as $\alpha/(4 \pi \varepsilon_{0})$, which
has unit of \AA. We find that $\alpha^{\parallel}$ has a general
descending trend when $E_{\mathrm{g}}$ increases. On the other hand,
no apparent trend between $\alpha^{\perp}$ and $E_{\mathrm{g}}$ is
observed (see Supplementary Section S2.2), which appears to be in good
agreement with our polarizability-based theoretical model. We now
validate Eq. \ref{eq:2D-Moss-para} and \ref{eq:2D-Moss-perp} using the
polarizabilities calculated by first principle calculations. Figure
\ref{fig-3}b shows $(4 \pi \varepsilon_{0})/\alpha^{\parallel}$ (in
\AA{}) as a function of $E_{\mathrm{g}}$ (in eV) for the 2D materials
investiaged (circle dots), with a linear regression slope of ~0.182
and $R^{2}$ of 0.84. From Ref. \citenum{Jiang_2017_Eg_Eb}, the slope
between $(4 \pi \varepsilon_{0})/\alpha^{\parallel}$ and $E_{g}$ is
$8\pi^{2}\varepsilon_{0} \mathrm{\AA}/(eN) \approx 0.436/N$, which
yields $N$ betweem 2 and 3, which is reasonable for the 2D materials
studied. We observe that materials with lower $E_{\mathrm{g}}$ ($<$4
eV) generally lie close to the regression line, while the deviation
becomes greater for materials with $E_{\mathrm{g}}>$4 eV, which has
also been observed in the $E_{\mathrm{b}}-E_{\mathrm{g}}$ relation of
2D materials \cite{Olsen_2016_hydrogen,Jiang_2017_Eg_Eb}. We also
discover that the linearity between
$(4 \pi \varepsilon_{0})/\alpha^{\parallel}$ and $E_{\mathrm{g}}$ is
better when the bandgap is calculated using the HSE06 hybrid
functionals, compared with that from the Perdew--Burk--Ernzerhof (PBE)
exchange correlations (details see Supplementary Section S2 and
Supplementary Figure S5), which can be explained by the fact that the
electronic structure, in particular the bandgap, is generally better
predicted at HSE06 level than PBE level \cite{Heyd_2005}. It should be
noted that although even more accurate estimation of both
$\varepsilon$ and $E_{\mathrm{g}}$ can be achieved via many-body
Green’s function method (GW) together with the Bethe-Salpeter equation
(BSE), the convergence of such method is known to be highly affected
by the dielectric screening of 2D materials
\cite{Hueser_2013_2Dvs3D}. Combining the accuracy, computational
effort and convergence, the choice of the HSE06 hybrid functional may
be most suitable to present the true 2D Moss-like relationship between
$\alpha^{\parallel}$ and $E_{\mathrm{g}}$.

We further examine the relation between $\alpha^{\perp}$ and the
thickness of a 2D material proposed in
Eq. \ref{eq:2D-Moss-perp}. Here we choose the ``covalent'' thickness
$\delta_{\mathrm{cov}}$ of a 2D material, which is defined as the
longest distance along the z-direction between any two atom nuclei
plus their covalent radii:
\begin{equation}
  \label{eq:cov-thick}
  \delta_{\mathrm{cov}} = \mathrm{max}(|z^{i} - z^{j}|
  + r^{i}_{\mathrm{cov}} + r^{j}_{\mathrm{cov}})
\end{equation}
where i, j are two atoms in the 2D material and $r_{\mathrm{cov}}^{i}$
is the covalent radius of atom i (Figure \ref{fig-3}c inset). As shown
in Figure \ref{fig-3}c, $\alpha^{\perp}/(4 \pi \varepsilon_{0})$
indeed shows an excellent linear correlation with
$\delta_{\mathrm{cov}}$, with $R^{2}=0.98$, and the slope very close
to $1/4\pi$. In addition to our theoretical predictions discussed
above, the perfect linear correlation between $\alpha^{\perp}$ and
$\delta_{\mathrm{cov}}$ has its strong physical meaning. Similar to
the molecular polarizability which characterizes the volume of
electron cloud of an isolated molecule \cite{Israelachvili_2011}, the
2D polarizability also characterizes the volume of the electron cloud
per unit area (from its definition), and naturally represents the
thickness of the electron cloud of the 2D material. The fact that the
thickness of the electron cloud can be approximated by the extension
of valence states in the z-direction, explains the close match between
the linear slope in Figure \ref{fig-3}c and $1/4\pi$ (see
Supplementary Section S4.1). In other words, the universal scaling
relation for $\alpha^{\perp}$ indicates the quantity
$\alpha^{\perp}/\varepsilon_{0}$, is the dielectric characteristic
thickness of a 2D material. We propose that the experimental
measurment of the electronic polarizability
\cite{Antoine_1999,Cherniavskaya_2003,Krauss_1999_EFM}, can also be
extended to measure $\alpha^{\perp}$ of a 2D material, as a direct
estimation of it thickness, in comparison with the optical
ellipsometry techniques \cite{Weber_2010} widely used to estimate the
thickness of 2D materials, which requires empirical optical model and
parameter fitting.

The universal relations of 2D polarizabilities are not
coincidence. Combining recent theoretical findings of the linear
relation between exciton binding energy $E_{\mathrm{b}}$ and
$E_{\mathrm{g}}$ of 2D materials
\cite{Choi_linear_2015,Olsen_2016_hydrogen,Jiang_2017_Eg_Eb}, and the
fact that the $E_{\mathrm{b}}$ is roughly inversely proportional to
$\alpha^{\parallel}$ \cite{Pulci_2014}, it is reasonable to have a
general Moss-like relation between $E_{\mathrm{g}}$ and
$1/\alpha^{\parallel}$. Moreover, the bandgap-independent relation of
2D $\alpha^{\perp}$ resembles molecular polarizabilities of conjugate
molecules \cite{Davies_1952}, fullerenes \cite{Sabirov_2014} and
carbon nanotubes \cite{Benedict_1995}, which are also shown to be
geometry-dependent. To rule out the possibility that our conclusion is
limited by the number of materials used, we further validate our
proposed 2D Moss-like relations on the recently-published C2DB
database \cite{Haastrup_2018}, from which we extracted the dielectric
properties of over 230 2D materials calculated at the PBE level, and
overlap them with our results in Figure \ref{fig-3}b and \ref{fig-3}c
(further details see Supplementary Section S3). Althought the
dielectric properties may be overestimated at PBE level due to
underestimation of the bandgap compared with the more accurate HSE06
functionals, apparent linear trends can be observed for both
$\alpha^{\parallel}$ and $\alpha^{\perp}$, with the linear coefficient
very close to the HSE06 results. Therefore, the proposed universal 2D
Moss-like relations are confirmed.  We have also tested the potential
relation between the 2D polarizabilities with other physical
quantities, including the effective carrier mass, quantum capacitance
and total atomic polarizabilities, while no apparent correlations are
found (details see Supplementary Section S3).

In short, we have revealed the 2D analog of the Moss relation by both
theoretical modeling and first principles calculations:
$\alpha^{\parallel}$ is inversely proportional to the minimal bandgap
$E_{\mathrm{g}}$, while $\alpha^{\perp}$ is the characteristic
thickness of the 2D material. Although their apparent forms in
Eq. \ref{eq:2D-Moss-para} and \ref{eq:2D-Moss-perp} seem different, we
will show the 2D Moss-like relations stem from the same origin. In
merit of the unit analysis, $\alpha^{\parallel}$ and $\alpha^{\perp}$
both have unit of $4\pi\varepsilon_{0} \cdot$[Length]. Specifically,
$\alpha^{\parallel}$ and $\alpha^{\perp}$ corresponds to
characteristic lengthes in- and out-of-plane, respectively. The
in-plane screened electrostatic potential $V(r)$ from a point charge
in an 2D plane, as a function of distance $r$:
$V(r) = {\displaystyle \frac{e}{4 \alpha^{\parallel}}}
\left[H_{0}({\displaystyle \frac{2\varepsilon_{0}
      r}{\alpha^{\parallel}}}) - Y_{0}( {\displaystyle \frac{2
      \varepsilon_{0}r}{\alpha^{\parallel}}})\right]$
\cite{Keldysh_1979_eps_multi,Pulci_2014}, where $H_{0}$ is the Struve
function and $Y_{0}$ is the Bessel function of second kind, is
assciated with the in-plane screening radius
$r_{0}^{\parallel}=\alpha^{\parallel}/(2 \varepsilon_{0})$, such that
$V(r,r/r^{\parallel}_{0} \gg 1)$ reduces to the simple Coulombic
potential in vacuum. Combining with the result that the thickness of
2D material is characterized by $\alpha^{\perp}/\varepsilon_{0}$, we
have drawn a generalized picture of the dielectric nature of 2D
materials via the 2D polarizability: the dielectric screening of a
point charge sitting in the middle of a 2D material can be viewed as
an ellipsoid with the length of principle axes to be
$\alpha^{\parallel}/(2 \varepsilon_{0})$ and
$\alpha^{\perp}/(2 \varepsilon_{0})$, respectively, analog to the
polarizability ellipsoid picture of molecules used in spectroscopy
\cite{Banwell_1994} (see Supplementary Figure S12). The in-plane
screening length is generally larger for a smaller bandgap
semiconductor, which qualitatively explains the inverse propotional
relation between $\alpha^{\parallel}$ and $E_{\mathrm{g}}$, a 2D
version of the Moss-relation.

@@

% \begin{figure}[htbp]
% \centering
% \includegraphics[width=0.5\linewidth]{img/fig-delta.pdf}
% \caption{\label{fig-delta} Scheme for the determination of the
  % covalent thickness of one-atom-thick (left) and few-atom-thick
  % (right) 2D materials.}
% \end{figure}

>>>>

Eqs. \ref{eq:def-eps-1} and \ref{eq:def-eps-2}, we can relate the 2D polarizabilities,
$\alpha_{\mathrm{2D}}^{\parallel}$ and $\alpha_{\mathrm{2D}}^{\perp}$ with $\varepsilon_{\mathrm{SL}}^{\parallel}$ and $\varepsilon_{\mathrm{SL}}^{\perp}$, respectively:

@@

  &\varepsilon_{\mathrm{SL}}^{\parallel} &= 1 + \frac{\alpha_{\mathrm{2D}}^{\parallel}}{\varepsilon_{0}L}\\
  &\varepsilon_{\mathrm{SL}}^{\perp} &= \left(1 - {\displaystyle \frac{\alpha_{\mathrm{2D}}^{\perp}}{\varepsilon_{\mathrm{0}} L}} \right)^{-1}

@@

\subsection{2D Moss-like  Relations}
\label{sec:first-principles}
Based on the 2D polarizabilities, we then investigate the potential
Moss-like relations for 2D materials. By evaluating the expressions
for $\alpha_{\mathrm{2D}}^{\parallel}$ and
$\alpha_{\mathrm{2D}}^{\perp}$ using Random Phase Approximation (RPA)
theory \cite{Adler_1962} with $\mathbf{k} \cdot \mathbf{p}$
treatment\cite{kittel_2005_introduction} (details see Supplementary
Section SXX) \todo{note}, we show that
$\alpha_{\mathrm{2D}}^{\parallel}$ and $\alpha_{\mathrm{2D}}^{\perp}$
have simple relation with the electronic  and structural information of a 2D
material, respectively:
\begin{subequations}
\begin{eqnarray}
\label{eq:2D-Moss-para}
  &\alpha^{\parallel} &\propto E_{g}^{-1} \\
  \label{eq:2D-Moss-perp}
  &\alpha^{\perp} & \propto \delta
\end{eqnarray}
\end{subequations}
where $E_{\mathrm{g}}$ is the minimal electronic bandgap of the 2D
material, and $\delta$ is its intrinsic
thickness. Eqs. \ref{eq:2D-Moss-para} and \ref{eq:2D-Moss-perp} are
the main conclusions of this work.

To validate such relations, we study several types of 2D materials as
show in Figure \ref{fig-3}a, including transition metal
dichalcogenides (TMDCs, with the formula MX\(_{\text{2}}\), where M is
a metal in group 4, 6, 10 and X=O, S, Se, Te), metal monochalcogenides
(Ga$_{2}$S$_{2}$, Ga$_{2}$Se$_{2}$), cadmium halides (CdX$_2$, X=Cl,
I), hexagonal boron nitride (BN), graphene derivatives (fluorographene
(C$_{2}$F$_{2}$), graphane (C$_{2}$H$_{2}$)), phosphorene (P$_{4}$)
and thin layer organic-inorganic perovskites (ABX$_{3}$).  For the
TMDCs, we consider 2 lattice phases, namely the 2H (P\(\bar{6}\)m2
space group) and 1T (P3m1 space group).  The static 2D
polarizabilities are calculated from the static dielectric response of
the selected 2D materials using density functional theory (DFT) with
the Heyd-Scuseria-Ernzerhof hybrid functionals (HSE06) using the
Vienna Ab Initio Simulation Package (VASP) including spin-orbit
coupling to avoid limitations on the description of band gaps and
dielectric functions (see Methods for details). Figure \ref{fig-3}b
shows the calculated $E_{\mathrm{g}}$ (blue dots) and polarizabilities
(bar plots) of all the 2D materials investigated, covering a wide
spectrum range from far infrared to ultraviolet. Note from dimension
analysis, it is more intuitive to express the polarizability as
$\alpha_{\mathrm{2D}}/(4 \pi \varepsilon_{0})$, which has unit of
\AA. We find that $\alpha_{\mathrm{2D}}^{\parallel}$ has a general
descending trend when $E_{\mathrm{g}}$ increases. On the other hand,
no apparent correlation between $\alpha_{\mathrm{2D}}^{\perp}$ and
$E_{\mathrm{g}}$ is observed (see Supplementary Section S2.2), which
appears to be in good agreement with our polarizability-based
theoretical model (Supplementary Section SXX \todo{note}). We then
examine Eqs. \ref{eq:2D-Moss-para} and \ref{eq:2D-Moss-perp} using the
polarizabilities calculated by first principle calculations. Figure
\ref{fig-3}b shows
$(4 \pi \varepsilon_{0})/\alpha_{\mathrm{2D}}^{\parallel}$ (in
\AA{}$^{-1}$) as a function of $E_{\mathrm{g}}$ (in eV) for the 2D
materials investiaged (circle dots), with a linear regression
coefficient of regression $R^{2}$ of 0.84, and a slope of 0.18, which
corresponds well with theoretical investigations
\citenum{Jiang_2017_Eg_Eb} (details see Supplementary Section SXX
\todo{format Jiang's paper into SI}).
% From Ref. \citenum{Jiang_2017_Eg_Eb}, the slope between
% $(4 \pi \varepsilon_{0})/\alpha^{\parallel}$ and $E_{g}$ is
% $8\pi^{2}\varepsilon_{0} \mathrm{\AA}/(eN) \approx 0.436/N$, which
% yields $N$ betweem 2 and 3, which is reasonable for the 2D materials
% studied.
% We observe that materials with lower $E_{\mathrm{g}}$ ($<$4
% eV) generally lie close to the regression line, while the deviation
% becomes greater for materials with $E_{\mathrm{g}}>$4 eV, which has
% also been observed in the $E_{\mathrm{b}}-E_{\mathrm{g}}$ relation of
% 2D materials \cite{Olsen_2016_hydrogen,Jiang_2017_Eg_Eb}.
We also discover that the linearity between
$(4 \pi \varepsilon_{0})/\alpha_{\mathrm{2D}}^{\parallel}$ and $E_{\mathrm{g}}$
(measured by the $R^{2}$ value) is higher when the bandgap is
calculated using the HSE06 hybrid functionals, compared with that from
the Perdew--Burk--Ernzerhof (PBE) exchange correlations (details see
Supplementary Section S2 and Supplementary Figure S5), which can be
explained by the fact that the electronic structure, in particular the
bandgap, is generally better predicted at HSE06 level than PBE level
\cite{Heyd_2005}. It should be noted that although even more accurate
estimation of both dielectric properties and bandgap can be achieved
via many-body Green’s function method (GW) together with the
Bethe-Salpeter equation (BSE), the convergence of such method is known
to be highly affected by the dielectric screening of 2D materials
\cite{Hueser_2013_2Dvs3D}. Combining the accuracy, computational
effort and convergence, the choice of the HSE06 hybrid functional may
be most suitable to present the true 2D Moss-like relationship between
$\alpha_{\mathrm{2D}}^{\parallel}$ and $E_{\mathrm{g}}$.
\todo[inline]{check the values for optical bandgap}

We further examine the relation between $\alpha^{\perp}$ and the
thickness of a 2D material proposed in
Eq. \ref{eq:2D-Moss-perp}. Here we choose the ``covalent'' thickness
$\delta_{\mathrm{cov}}$ of a 2D material, which is defined as the
longest distance along the z-direction between any two atom nuclei
plus their covalent radii:
\begin{equation}
  \label{eq:cov-thick}
  \delta_{\mathrm{cov}} = \mathrm{max}(|z^{i} - z^{j}|
  + r^{i}_{\mathrm{cov}} + r^{j}_{\mathrm{cov}})
\end{equation}
where i, j are two atoms in the 2D material and $r_{\mathrm{cov}}^{i}$
is the covalent radius of atom i (Figure \ref{fig-3}c inset). As shown
in Figure \ref{fig-3}c,
$\alpha_{\mathrm{2D}}^{\perp}/(4 \pi \varepsilon_{0})$ indeed shows an
excellent linear correlation with $\delta_{\mathrm{cov}}$, with
$R^{2}=0.98$, and the slope very close to $1/4\pi$. In other words,
$\alpha_{\mathrm{2D}}^{\perp} / \varepsilon_{0}$ is almost identical
to $\delta_{\mathrm{cov}}$, which has its strong physical
meaning. Similar to the molecular polarizability which characterizes
the volume of electron cloud of an isolated molecule
\cite{Israelachvili_2011},
$\alpha_{\mathrm{2D}}^{\perp}/\varepsilon_{0}$ is also related to the
volume of the electron cloud per unit area (from its definition), and
is naturally proportional to the electron cloud thickness of the 2D
material (see Supplementary Section SXX). In fact, the universal
scaling relation for $\alpha^{\perp}$ in Figure \ref{fig-3}c indicates
that the quantity $\alpha^{\perp}/\varepsilon_{0}$ measurable via
electronic approaches
\cite{Antoine_1999,Cherniavskaya_2003,Krauss_1999_EFM}, is indeed the
(dielectric) characteristic thickness of a 2D material, and can be
used to resolve the long-existing controversy about the experimental
thickness of 2D materials, such as graphene \cite{Shearer_2016}.

\iffalse
The universal relations for $\alpha_{\mathrm{2D}}^{\parallel}$ and
$\alpha_{\mathrm{2D}}^{\perp}$ revealed by Eqs. \ref{eq:2D-Moss-para}
and \ref{eq:2D-Moss-perp} are not coincidence. Combining recent
theoretical findings of the linear relation between exciton binding
energy $E_{\mathrm{b}}$ and $E_{\mathrm{g}}$ of 2D materials
\cite{Choi_linear_2015,Olsen_2016_hydrogen,Jiang_2017_Eg_Eb}, and the
fact that the $E_{\mathrm{b}}$ is roughly inversely proportional to
$\alpha^{\parallel}$ \cite{Pulci_2014}, it is reasonable to have a
general Moss-like relation between $E_{\mathrm{g}}$ and
$1/\alpha^{\parallel}$. Moreover, the bandgap-independent relation of
2D $\alpha^{\perp}$ resembles molecular polarizabilities of conjugate
molecules \cite{Davies_1952}, fullerenes \cite{Sabirov_2014} and
carbon nanotubes \cite{Benedict_1995}, which are also shown to be
geometry-dependent.
\fi

To rule out the possibility that our conclusion is limited by the
number of materials used, we further validate our proposed 2D
Moss-like relations on the recently-published C2DB database
\cite{Haastrup_2018}, from which we extracted the dielectric
properties of over 230 2D materials calculated at the PBE level, and
superimpose with our results in Figure \ref{fig-3}b and \ref{fig-3}c
(details see Supplementary Section S3). Althought the dielectric
properties may be overestimated at PBE level due to underestimation of
the bandgap compared with the more accurate HSE06 functionals
\cite{Van_Dyck_2017}, similar linear trends can be observed for both
$\alpha^{\parallel}_{\mathrm{2D}}$ and $\alpha_{\mathrm{2D}}^{\perp}$,
with the linear coefficient very close to the HSE06 results. We have
also tested the potential relation between the 2D polarizabilities
with other physical quantities, including the effective carrier mass,
quantum capacitance and total atomic polarizabilities, while no
apparent correlations are found (details see Supplementary Section
S3).

In short, we have revealed the 2D analog of the Moss relation by both
theoretical modeling and first principles calculations:
$\alpha_{\mathrm{2D}}^{\parallel}$ is inversely proportional to the
minimal bandgap $E_{\mathrm{g}}$, while $\alpha_{\mathrm{2D}}^{\perp}$
is the characteristic thickness of the 2D material. Next we show,
despite their different forms, both 2D Moss-like relations stem from
the same origin. In merit of the unit analysis,
$\alpha_{\mathrm{2D}}^{\parallel}$ and $\alpha_{\mathrm{2D}}^{\perp}$
both have unit of $4\pi\varepsilon_{0} \cdot$[Length], or in other
words, $\alpha_{\mathrm{2D}}^{\parallel}$ and
$\alpha_{\mathrm{2D}}^{\perp}$ correspond to in- and out-of-plane
characteristic lengthes, respectively. The in-plane screened
electrostatic potential $V(r)$ from a point charge in an 2D plane, as
a function of distance $r$:
$V(r) = {\displaystyle \frac{e}{4 \alpha^{\parallel}}}
\left[H_{0}({\displaystyle \frac{2\varepsilon_{0}
      r}{\alpha^{\parallel}}}) - Y_{0}( {\displaystyle \frac{2
      \varepsilon_{0}r}{\alpha^{\parallel}}})\right]$
\cite{Keldysh_1979_eps_multi,Pulci_2014}, where $H_{0}$ is the Struve
function and $Y_{0}$ is the Bessel function of second kind, is
associated with the in-plane screening radius
$r_{0}^{\parallel}=\alpha_{\mathrm{2D}}^{\parallel}/(2
\varepsilon_{0})$, such that $V(r,r/r^{\parallel}_{0} \gg 1)$ reduces
to the simple Coulombic potential in vacuum. Combining with the result
that $\alpha_{\mathrm{2D}}^{\perp}/\varepsilon_{0}$ characterizes the
thickness of a 2D material, we have drawn a generalized picture of the
dielectric nature of 2D materials via the 2D polarizability: the
dielectric screening of a point charge sitting in the middle of a 2D
material can be viewed as an ellipsoid with the length of principle
axes to be
$r_{0}^{\parallel} = \alpha_{\mathrm{2D}}^{\parallel}/(2
\varepsilon_{0})$ and
$r_{0}^{\perp} = \alpha^{\perp}_{\mathrm{2D}}/(2 \varepsilon_{0})$,
respectively, analog to the polarizability ellipsoid picture of
molecules used in spectroscopy \cite{Banwell_1994} (see Supplementary
Figure S12). The polarizability ellipsoid for a 2D material is in
general ultra flat, with $r_{0}^{\parallel} \gg r_{0}^{\perp}$, as
can be seen from the group 6 TMDCs in Table \ref{tbl:radii}.
Moreover, $r_{0}^{\parallel}$ is generally larger for a smaller
bandgap semiconductor, which qualitatively explains the inverse
propotional relation between $\alpha^{\parallel}$ and
$E_{\mathrm{g}}$, a 2D version of the Moss-relation.

@@

% \begin{figure}[htbp]
% \centering
% \includegraphics[width=0.5\linewidth]{img/fig-delta.pdf}
% \caption{\label{fig-delta} Scheme for the determination of the
  % covalent thickness of one-atom-thick (left) and few-atom-thick
  % (right) 2D materials.}
  % \end{figure}
\begin{table}[htbp]
  \centering
  \caption{In-plane ($r_{0}^{\parallel}$) and out-of-plane
    ($r_{0}^{\perp}$) radii of the polarizability ellipsoid of
    selected 2D materials calculated from first principles
    simulations. $r_{0}^{\parallel}$ is in general much larger than
    $r_{0}^{\perp}$, which accounts for the highly anisotropic
    dielectric nature of 2D materials.}
  \label{tbl:radii}  
  \begin{tabular}[htbp]{lcc}
    \hline
    Material & $r_{0}^{\parallel} = \alpha_{\mathrm{2D}}^{\parallel}/2\varepsilon_{0}$ (\AA{}) &  $r_{0}^{\perp} = \alpha_{\mathrm{2D}}^{\perp}/2\varepsilon_{0}$ (\AA{})\\
    \hline
    2H-MoS$_{2}$ & 40.0 & 2.50 \\
    2H-MoSe$_{2}$ & &  \\
    2H-MoTe$_{2}$ & 58.1 & 3.07  \\
    2H-WS$_{2}$ & 35.7 & 2.46  \\
    2H-WSe$_{2}$ & 41.0 & 2.71 \\
    2H-WTe$_{2}$ & 53.5 &  3.17\\
    \hline
  \end{tabular}
\end{table}
